Dark matter halo shape in the Auriga simulations: radial dependence, time evolution and baryon disk alignment

### 2019-07-17 Document/paper.tex
edit

The results by \cite{Bovy16} (BBFK16 hereafter) have the same general approach but use
instead the GD-1 \citep{2006ApJ...641L..37G} and Pal 5 \citep{2009AJ....137.3378O}
streams to constraint the shape of the dark matter component of the
galacic halo potential.
They use general models with large degrees of freedom for the galactic
potential in order to measure to what extent these two streams are sensitive
to the triaxiality of the dark matter halo component.
The DM component is written directly as a triaxial density profile
with coaxial ellipsoids and the corresponding potential is found by
numerical integration.
They find that the width of the Pal 5 stream constraints $b/a\approx
1$ and therefore fix it to $b/a=1$, finally they report their most stringent
constrain of $c/a=0.93\pm0.16$ at a radius of $\approx 19$kpc from the
Pal 5 stream.

Our Figure \label{fig:observations} shows an explicit comparison in
the $c/a$-$b/a$ plane of the results by LM10

>>>>

The results by \cite{Bovy16} (BBFK16 hereafter) have the same general approach but use
instead the GD-1 \citep{2006ApJ...641L..37G} and Pal 5 \citep{2009AJ....137.3378O}
streams to constraint the shape of the dark matter component of the
galacic halo potential.
They use general models with large degrees of freedom for the galactic
potential in order to measure to what extent these two streams are sensitive
to the triaxiality of the dark matter halo component.
The DM component is written directly as a triaxial density profile
with coaxial ellipsoids and the corresponding potential is found by
numerical integration.
They find that the width of the Pal 5 stream constraints $b/a\approx
1$ and therefore fix it to $b/a=1$, finally they report their most stringent
constrain of $c/a=0.93\pm0.16$ at a radius of $\approx 19$kpc from the
galactic center.

Our Figure \label{fig:observations} shows an explicit comparison in
the $c/a$-$b/a$ plane against the results by LM10 and BBFK16. 
We find $6$ halos with $b/a<0.93$ and $c/a>0.77$ that could be
considered consistent with their shape constraints 
by BBFK16.
In contrast, none of the simulated halos is consistent with the LM10
results.

The results by LM10 would place then the dark matter halo of our Milky
Way as an extreme outlier in the $\Lambda$ CDM model. 
This extreme prolateness also correlateswith the extreme
triaxiality of the 11 classical satellites of the MW ($c/a\approx
0.2$, and $b/a\approx0.9$) with an spatial distribution 
also oriented perpendicular to the MW plane, another highly unusual
feature in the $\Lambda$ CDM model \citep{2018MNRAS.478.5533F}
